Parallel Hierarchical Clustering using \\ Rank-Two Nonnegative Matrix Factorization \thanks{Identify applicable funding agency here. If none, delete this.}

### 2020-07-15 latex/paper.tex
scaled the dc figure and fixed latex bug
adding notes for experimental analysis

@@

@@

@@

\GB{3 plots: for synthetic level breakdown for 1 node and for 40 nodes; for realworld just for 80 nodes

@@

>>>>

\GB{specify that $\imath=\jmath=100$ in all experiments, also what do we set $k$ to be?  fixed number for each dataset?  any other experimental parameters we should specify?}

@@

\begin{itemize}
	\item theory says...
	\item Figs 3 and 5 show performance relative to the smallest number of nodes required to store data and factor matrices
	\item strong scaling is nearly linear, see 49X (check number) on 50 nodes for synthetic data and 7.3X (check number) on 80 nodes for image data
	\item Figs 4 and 6 show time breakdown, explain scaling: MM scales perfectly because it's mem-bw bound and the local problem size decreases linearly, bandwidth cost is fixed relative to $p$, so relative cost grows as we scale; comm is bandwidth bound because we see all-gather and reduce-scatter dominate all-reduce
\end{itemize}

@@

\GB{Do these breakdowns include the score function?  actually this may explain why all-reduce costs more, it also has $O(n)$ data for score...}

\GB{4 plots: 2 data sets with speedup/breakdown, note that we include time for complete levels, ignoring nodes in incomplete levels for easier interpretation}

\begin{itemize}
	\item theory says...t
	\item Fig 7 shows limit of strong scaling for synthetic data (time increases at 50 nodes compared to 40), Fig 8 gives breakdown and explains
	\begin{itemize}
		\item drastic performance dropoff may be artifact of all-gather, which should take about the same time as reduce-scatter, but speedup from 30 to 40 nodes is also slight
		\item by 50 nodes, about 50\% of time in communication; still mostly dominated by bandwidth cost because ag and rs dominate ar
		\item note the difference between the scaling of single rank-2 and entire tree: poor scaling must be due to lower levels, which we explore in the next section
	\end{itemize}
	\item Fig 9 shows reasonable scaling for entire tree -- speedup drops from 7x to 6x over 80 nodes; Fig 10 shows that MM is still 70\% of run time on 80 nodes, which allows for near-linear scaling
\end{itemize}

@@

\GB{3 plots: for synthetic level breakdown for 1 node and for 40 nodes; for realworld just for 80 nodes}

\begin{itemize}
	\item theory says 
\end{itemize}

@@

\begin{itemize}
	\item consider sparse case
	\item consider parallelizing across tree
	\item consider redistribution for 2D
\end{itemize}
